---
title: "Plausibility bounds"
output: pdf_document
---

```{r echo=FALSE, results='hide',message=FALSE}
rm(list=ls()) # clean environment

# Data manipulation packages
library(here) 
library(data.table)
library(dplyr)
require(knitr)
```


```{r echo=FALSE, results='hide',message=FALSE}
data <- as.data.table(read.csv(here('1_Input_data','pilot10_08SEP21_withmetadata.csv'), stringsAsFactors=FALSE, fileEncoding="latin1"))
infoexp <- as.data.table(readxl::read_xlsx(here('1_Input_data','Infoexp.xlsx'),sheet="Table")) #CSV file with the

base.dir <- dirname(dirname(rstudioapi::getActiveDocumentContext()$path)) # set main base working directory
setwd(base.dir)

data<-as.data.table(read.csv('1_Input_data/pilot10_08SEP21_withmetadata.csv', stringsAsFactors=FALSE, fileEncoding="latin1"))

infoexp<-as.data.table(readxl::read_xlsx("1_Input_data/Infoexp.xlsx",sheet="Table")) #Table in which the included variables are specified according Expert opinion, also includes the order in which variables are imputed 
var_inc<-infoexp[Inclusion==1,Variable] #Variables to work with
data<-as.data.table(data[,..var_inc]) #Filter dataset

#1. Initial clean up the dataset -----
#1.0. Check for duplicates ----
data[,comb:=paste0(studyname,mid_original,sep="_")] #create a variable that combines study and patient id
n_occur <- data.table(table(data$comb))
#n_occur[n_occur$N>1] #check visually which observations are duplicated
var1<-n_occur[n_occur$N > 1&V1!='_Spain_Soriano'& V1!='_TrinidadTobago_Sohan']$V1 
var1<-n_occur[n_occur$N > 1]$V1
Duplicates<-data[comb%in%var1&multiplegest!=1] # table to report to harmonization team.
write.csv(Duplicates,file='5_Internal_support/Possible_duplicates.csv')

# 1.1. Check format of categorical variables----
char <-   which(sapply(data, is.character)) #which are character
datac<-data[,..char]
summary(datac)
unique(datac$inf_head_circ_age_fu1)
data[,inf_head_circ_age_fu1:=as.numeric(sub(" .*", "",data$inf_head_circ_age_fu1))] # remove years
data[,zikv_elisa_ga_1:=as.numeric(sub(" .*", "",data$zikv_elisa_ga_1))] #remove weeks

#unique(data$othabnorm_spec) # 39 categories ask if really want to include this
#data[,othabnorm_spec:=NULL] # We temporally remove it from dataset as it is messy
data[zikv_pcr_date_1%in%c("22027","888",""), zikv_pcr_date_1:=NA]
data[zikv_elisa_date_1%in%c(""),zikv_elisa_date_1:=NA]
data[symp_date%in%c(""),symp_date:=NA]
data[,arb_clindiag:=ifelse(arb_clindiag==777,6,arb_clindiag)] # We set the NA value ("777") to a level "6" because we later use it to define CZS variable

#1.1. Set to NA : 666,777,888,999 values----
data[data==""] <-NA
data[data==666] <-  NA
data[data==777] <-  NA
data[data==888] <-  NA
data[data==999] <-  NA
data[data==9999] <-  NA

data[,Comb_id:=paste(studyname,mid_original,childid_original,sep="-")] #combined ID from study mother and child id
```

In this document we describe the plausible values that are considered for each of the variables used in the imputation model. In addition we provide the rules that we applied on the creation of additional variables required for the imputation model.

## Plausibility bounds 
The following table describes the plausibility bounds for the continuous variables and the time-related variables used in the imputation process. There you can see for each variable, the classification, the units and the plausibility bounds (minimum, maximum). We plan to set all values outside the plausible bounds as NA.
```{r functions,echo=F}
Boundaries<-infoexp[Inclusion==1&Vtype%in%c("C","T"),c("Type","Variable","Vtype","Units","Min","Max")]
Boundaries[,Vtype:=ifelse(Vtype=="C","Continuous","Time")]
Boundaries[,Max:=ifelse(is.na(Max),"Inf",Max)]
knitr::kable(Boundaries, 
             col.names = c("Classification",
                           "Variable name",
                           "Variable type",
                           "Units",
                           "Min",
                           "Max"))

```

By running this code, the "obs_to_check.RData" file is automatically generated with the observations outside the plausibility range. It can be found in the "3_Output_data" file. Inside the obs_to_check dataset, there is an additional column called "Var_to_check" that indicates the variable with possible implausible values for each observation.

```{r,echo=FALSE}
boundvar=Boundaries$Variable
obs_to_check<-NULL
for(var in boundvar){
  data$var_bound<-data[,..var]
  data$Var_to_check<-var
  Min=as.numeric(Boundaries[Variable==var]$Min)
  Max=as.numeric(ifelse(is.na(Boundaries[Variable==var]$Max),1/0,Boundaries[Variable==var]$Max))
  data_out<-data[var_bound<=Min|var_bound>=Max]
  obs_to_check<-rbind(obs_to_check,data_out)
}    

save(obs_to_check,file=here('3_Output_data','obs_to_check.RData'))
```


## Logic rules for exposures

# Set to NA values
SAS and R manage missing values differently. To make the imputation process easier, we set to NA all values equal to 666,777,888,999. Except for the arb_clindiag varaible, for which "777" values were assigned to a "6" level as it is used later on to define the CZS variable.

# Zika test time of measurement (zikv_ga)
In case the zikv_ga value is not specified for an observation, but the time of measurement for the PCR "zikv_pcr_ga_1" or the elisa test "zikv_elisa_ga_1" wás specified, we set the zikv_ga value with the date of measurement of the earliest test. 

if is.na (zikv_ga) then zikv_ga = min (zikv_pcr_ga_1,zikv_elisa_ga_1)

# Creation of new variables
For the following variables, we combine different variables in one general variable $x_{com}$in order to include the information in a simple way that helps us to avoid any imputation convergence problem. For instance if we want to create a new Xm variable that combines information of $x_1$,$x_2$,...,$x_n$. 
If for any of this $x_i$ variables with any response, there is the presence of a characteristic, outcome or a positive test $x_i==1$,then the new variable $x_{com}$ is assigned with overall presence.
  $$if (any (x_1==1, x_2==1,..x_n=1)) , then ,  x_{com}=1$$
In case that no presence is found for all the $x_i$ variables with any response then the $x_{com}$ is assigned to no presence. $$if (all (x_1==0, x_2==0,..x_n=0)) , then ,  x_{com}=0$$
If for a certain patient, there was no information on any of these $x_i$ variables then the observation is assigned to NA.\\
$$if (all (is.na(x_1), is.na(x_2),..is.na(x_n=1)) ,then,  x_{com}=NA$$

# storch_patho
Denotes the Intrauterine exposure to storch pathogens. It was created by combining the following variables with the previous explained rule. 

- ifelse(storch==0,0,ifelse(!is.na(storch),1,0))]
- storch_bin
- toxo
- toxo_treat
- syphilis
- syphilis_treat
- varicella
- parvo
- rubella
- cmv
- herpes
- listeria
- chlamydia
- gonorrhea
- genitalwarts

# arb_ever

It refers to the presence of a prior arb virus infection, and it combines the following variables: 

- ifelse(zikv_pcr_everpos==1,1,ifelse(zikv_pcr_everpos==0,0,NA))]
- zikv_elisa_everpos
- denv_ever
- chikv_ever

# flavi_alpha_virus
This variable denotes the presence of concurrent or prior flavi- or alpha virus infection, and we used the following variables to create it. 

- ifelse(arb_clindiag_plus==0,0,ifelse(!is.na(arb_clindiag_plus),1,0))
- ifelse(arb_clindiag!=0&arb_clindiag!=1,0,ifelse(!is.na(arb_clindiag),1,0))
- denv_ever
- chikv_ever

# arb_preg_nz

This variable is related to the presence of any arbo virus in the current pregnancy without considering zika virus.

- ifelse(arb_clindiag==0|arb_clindiag==1,0,ifelse(!is.na(arb_clindiag),1,NA))
- denv_preg
- chikv_preg

