---
title: "Plausible values and creation of new variables"
output: pdf_document
---

```{r echo=FALSE, results='hide',message=FALSE}
rm(list=ls()) # clean environment

# Data manipulation packages
library(here) 
library(data.table)
library(dplyr)
require(knitr)
```


```{r echo=FALSE, results='hide',message=FALSE}
data <- as.data.table(read.csv(here('1_Input_data','pilot10_08SEP21_withmetadata.csv'), stringsAsFactors=FALSE, fileEncoding="latin1"))
infoexp <- as.data.table(readxl::read_xlsx(here('1_Input_data','Infoexp.xlsx'),sheet="Table")) #CSV file with the

base.dir <- dirname(dirname(rstudioapi::getActiveDocumentContext()$path)) # set main base working directory
setwd(base.dir)

data<-as.data.table(read.csv('1_Input_data/pilot10_08SEP21_withmetadata.csv', stringsAsFactors=FALSE, fileEncoding="latin1"))

infoexp<-as.data.table(readxl::read_xlsx("1_Input_data/Infoexp.xlsx",sheet="Table")) #Table were are specified the included variables according Expert opinion, also the includes the order in which variables are imputed 
var_inc<-infoexp[Inclusion==1,Variable] #Variables to work with
data<-as.data.table(data[,..var_inc]) #Filter dataset

#1. Initial clean up the dataset -----
#1.0. Check for duplicates ----
data[,comb:=paste0(studyname,mid_original,sep="_")] #create a variable that combine study and patient id
n_occur <- data.table(table(data$comb))
#n_occur[n_occur$N>1] #check visually which observations are duplicated
var1<-n_occur[n_occur$N > 1&V1!='_Spain_Soriano'& V1!='_TrinidadTobago_Sohan']$V1 
var1<-n_occur[n_occur$N > 1]$V1
Duplicates<-data[comb%in%var1&multiplegest!=1] # table to report to harmonization team.
write.csv(Duplicates,file='5_Internal_support/Possible_duplicates.csv')

# 1.1. Check format of categorical variables----
char <-   which(sapply(data, is.character)) #which are char
datac<-data[,..char]
summary(datac)
unique(datac$inf_head_circ_age_fu1)
data[,inf_head_circ_age_fu1:=as.numeric(sub(" .*", "",data$inf_head_circ_age_fu1))] # remove years
data[,zikv_elisa_ga_1:=as.numeric(sub(" .*", "",data$zikv_elisa_ga_1))] #remove weeks

#unique(data$othabnorm_spec) # 39 categories ask if really want to include this
#data[,othabnorm_spec:=NULL] # We temporal remove it from dataset as it is messy
data[zikv_pcr_date_1%in%c("22027","888",""), zikv_pcr_date_1:=NA]
data[zikv_elisa_date_1%in%c(""),zikv_elisa_date_1:=NA]
data[symp_date%in%c(""),symp_date:=NA]
data[,arb_clindiag:=ifelse(arb_clindiag==777,6,arb_clindiag)] # We set the NA value ("777") to a level "6" because we later use it for define CZS variable

#1.1. Set to NA : 666,777,888,999 values----
data[data==""] <-NA
data[data==666] <-  NA
data[data==777] <-  NA
data[data==888] <-  NA
data[data==999] <-  NA
data[data==9999] <-  NA

data[,Comb_id:=paste(studyname,mid_original,childid_original,sep="-")] #combinated ID from study mother and child id
```

Under this document we describe the plausible values consider for each of the variables used in the imputation model. In addition we provide the rules that we applied on the creation of additional variables required for the imputation model.

## Considered plausible ranges
The following table describes the continuous variables and the time-related variables we require to run the imputation model. There you can see for each variable, the classification, the units and the plausible range (minimum, maximum). We set all values outside the plausible range as NA.
```{r functions,echo=F}
Boundaries<-infoexp[Inclusion==1&Vtype%in%c("C","T"),c("Type","Variable","Vtype","Units","Min","Max")]
Boundaries[,Vtype:=ifelse(Vtype=="C","Continuous","Time")]
Boundaries[,Max:=ifelse(is.na(Max),"Inf",Max)]
knitr::kable(Boundaries, 
             col.names = c("Classification",
                           "Variable name",
                           "Variable type",
                           "Units",
                           "Min",
                           "Max"))

```

By running this code, it is generated the "obs_to_check.RData" file with the observations outside the plausible range, it can be found in the "3_Output_data", there is an additional column called "Var_to_check" that indicates the variable with implausible values for each observation.

```{r,echo=FALSE}
boundvar=Boundaries$Variable
obs_to_check<-NULL
for(var in boundvar){
  data$var_bound<-data[,..var]
  data$Var_to_check<-var
  Min=Boundaries[Variable==var]$Min
  Max=Boundaries[Variable==var]$Max
  data_out<-data[var_bound<=Min|var_bound>=Max]
  obs_to_check<-rbind(obs_to_check,data_out)
}    

save(obs_to_check,file=here('3_Output_data','obs_to_check.RData'))
```



