---
title: "Assumptions for exposure variables"
output: pdf_document
---

```{r echo=FALSE, results='hide',message=FALSE}
rm(list=ls()) # clean environment

# Data manipulation packages
library(here) 
library(data.table)
library(dplyr)
require(knitr)
```


```{r echo=FALSE, results='hide',message=FALSE}
data <- as.data.table(read.csv(here('1_Input_data','pilot10_08SEP21_withmetadata.csv'), stringsAsFactors=FALSE, fileEncoding="latin1"))
infoexp <- as.data.table(readxl::read_xlsx(here('1_Input_data','Infoexp.xlsx'),sheet="Table")) #CSV file with the

base.dir <- dirname(dirname(rstudioapi::getActiveDocumentContext()$path)) # set main base working directory
setwd(base.dir)

data<-as.data.table(read.csv('1_Input_data/pilot10_08SEP21_withmetadata.csv', stringsAsFactors=FALSE, fileEncoding="latin1"))

infoexp<-as.data.table(readxl::read_xlsx("1_Input_data/Infoexp.xlsx",sheet="Table")) #Table in which the included variables are specified according Expert opinion, also includes the order in which variables are imputed 
var_inc<-infoexp[Inclusion==1,Variable] #Variables to work with
data<-as.data.table(data[,..var_inc]) #Filter dataset

#1. Initial clean up the dataset -----
#1.0. Check for duplicates ----
data[,comb:=paste0(studyname,mid_original,sep="_")] #create a variable that combines study and patient id
n_occur <- data.table(table(data$comb))
#n_occur[n_occur$N>1] #check visually which observations are duplicated
var1<-n_occur[n_occur$N > 1&V1!='_Spain_Soriano'& V1!='_TrinidadTobago_Sohan']$V1 
var1<-n_occur[n_occur$N > 1]$V1
Duplicates<-data[comb%in%var1&multiplegest!=1] # table to report to harmonization team.
write.csv(Duplicates,file='5_Internal_support/Possible_duplicates.csv')

# 1.1. Check format of categorical variables----
char <-   which(sapply(data, is.character)) #which are character
datac<-data[,..char]
summary(datac)
unique(datac$inf_head_circ_age_fu1)
data[,inf_head_circ_age_fu1:=as.numeric(sub(" .*", "",data$inf_head_circ_age_fu1))] # remove years
data[,zikv_elisa_ga_1:=as.numeric(sub(" .*", "",data$zikv_elisa_ga_1))] #remove weeks

#unique(data$othabnorm_spec) # 39 categories ask if really want to include this
#data[,othabnorm_spec:=NULL] # We temporally remove it from dataset as it is messy
data[zikv_pcr_date_1%in%c("22027","888",""), zikv_pcr_date_1:=NA]
data[zikv_elisa_date_1%in%c(""),zikv_elisa_date_1:=NA]
data[symp_date%in%c(""),symp_date:=NA]
data[,arb_clindiag:=ifelse(arb_clindiag==777,6,arb_clindiag)] # We set the NA value ("777") to a level "6" because we later use it to define CZS variable

#1.1. Set to NA : 666,777,888,999 values----
data[data==""] <-NA
data[data==666] <-  NA
data[data==777] <-  NA
data[data==888] <-  NA
data[data==999] <-  NA
data[data==9999] <-  NA

data[,Comb_id:=paste(studyname,mid_original,childid_original,sep="-")] #combined ID from study mother and child id
```

In this document we describe the range of plausible values considered for each of the variables used in the imputation model. In addition, we provide the rules we use for combination variables, which were created in order to include as much information in the model as possible without the need to add many variables with a high proportion of missing values. 

# Plausibility bounds
The following table describes the plausibility ranges for the continuous and time-related variables used in the imputation process. It shows the minimum and maximum value for each variable.  When an observation has values greater than or equal to the maximum value or less than or equal to the minimum value, we set the value of the variable out of range as NA. 

```{r functions,echo=F}
Boundaries<-infoexp[Inclusion==1&Vtype%in%c("C","T"),c("Type","Variable","Vtype","Units","Min","Max")]
Boundaries[,Vtype:=ifelse(Vtype=="C","Continuous","Time")]
Boundaries[,Max:=ifelse(is.na(Max),"Inf",Max)]
knitr::kable(Boundaries, 
             col.names = c("Classification",
                           "Variable name",
                           "Variable type",
                           "Units",
                           "Min",
                           "Max"),
             caption = "Plausibility bounds")

```

When running this code, the file "obs_to_check.RData" with the observations outside the plausibility range is automatically generated. This file contains all the information of the conflicting observations and additionally has the column "Var_to_check" with the name of the variable outside the limits and the column "Var_bound" with the possible outlier value. This file can be found in the folder "3_Output_data" in the folder "imputation process". 


```{r,echo=FALSE}
boundvar=Boundaries$Variable
obs_to_check<-NULL
for(var in boundvar){
  data$var_bound<-data[,..var]
  data$Var_to_check<-var
  Min=as.numeric(Boundaries[Variable==var]$Min)
  Max=as.numeric(ifelse(is.na(Boundaries[Variable==var]$Max),1/0,Boundaries[Variable==var]$Max))
  data_out<-data[var_bound<=Min|var_bound>=Max]
  obs_to_check<-rbind(obs_to_check,data_out)
}    

save(obs_to_check,file=here('3_Output_data','obs_to_check.RData'))
```

# Logical rules for exposures

## Set to NA values
SAS and R handle missing values differently. To facilitate the imputation process, we set to NA all values designated in the harmonisation process as 666,777,888,999. However, this assignment is not generalised as sometimes these NA values contain useful information in the definition of other variables.

## Zika test measurement time (zikv_ga)
In case the date of the Zika test "zikv_ga" is not specified but information about the date of the PCR test "zikv_pcr_ga_1" or the elisa test "zikv_elisa_ga_1" is available. We set the value of zika_ga as the earliest date of the PCR and ELISA tests. 
if is.na (zikv_ga) then zikv_ga = min(zikv_pcr_ga_1,zikv_elisa_ga_1)

After the last meeting with the exposures group, we will include the test value in the assignment, i.e. for tests with positive values, the date of the first positive test, and in case of tests with negative values, the date of the last test performed.

## Creation of combination variables
For the following variables, we combine different variables into a combination variable $x_{c}$ in order to include as much information as possible without affecting the imputation process. These variables try to describe globally the presence of a certain characteristic or disease in the subject. 

| Patient | x1 | x2 | x3 | xn | xc |
|---------|----|----|----|----|----|
| 1       | 1  | 0  | NA | NA | 1  |
| 2       | NA | 0  | NA | 0  | 0  |
| 3       | NA | NA | NA | NA | NA |
Table: Example of combination variable

For example, given the combination variable $x_c$ created from the variables $x_1$,$x_2$,...,$x_n$. We assign a presence value $x_m=1$, if any of the variables $x_i$ has a presence value $x_i=1$. (i.e. Patient 1, Table 2) 
$$if (any (x_1==1, x_2==1,..x_n=1)),  then , x_{c}=1.$$
We assign a non-presence value $x_m=0$ in case all variables has a non-presence value $x_i=0$ (i.e. Patient 2, Table 2). 
$$if (all (is.na(x_1), is.na(x_2),..is.na(x_n=1))) ,then, x_{c}=NA.$$
We assume that in case of missing values in some variable $x_i= NA$ its value is equal to non-presence $x_i=0$. When there are not observable values for all the $x_i$ we assign NA to the combination variable $x_c=NA$ (i.e. Patient 3, Table 2).

### 1. storch_patho
Denotes intrauterine exposure to storch pathogens. It was created by combining the following variables with the rule explained above. 


- ifelse(storch==0,0,ifelse(!is.na(storch),1,0))]
- storch_bin
- toxo
- toxo_treat
- syphilis
- syphilis_treat
- varicella
- parvo
- rubella
- cmv
- herpes
- listeria
- chlamydia
- gonorrhea
- genitalwarts

### 2. arb_ever

Refers to the presence of a previous arb virus infection, and the following variables were used to create it

- ifelse(zikv_pcr_everpos==1,1,ifelse(zikv_pcr_everpos==0,0,NA))]
- zikv_elisa_everpos
- denv_ever
- chikv_ever

### 3. flavi_alpha_virus
This variable denotes the presence of a concurrent or previous flavi or alpha virus infection, and we combine the following variables 


- ifelse(arb_clindiag_plus==0,0,ifelse(!is.na(arb_clindiag_plus),1,0))
- ifelse(arb_clindiag!=0&arb_clindiag!=1,0,ifelse(!is.na(arb_clindiag),1,0))
- denv_ever
- chikv_ever

### 4. arb_preg_nz

This variable is related to the presence of any arbovirus in the current pregnancy without considering zika virus, as the information on the presence of zika is found in the variable zika_preg.

- ifelse(arb_clindiag==0|arb_clindiag==1,0,ifelse(!is.na(arb_clindiag),1,NA))
- denv_preg
- chikv_preg

